---
name: Diana
surname: Villasana Ocampo
position: "Population researcher|Actuarial Science | Statitics"
address: "Mexico City, Mexico"
email: "dvillasanao@hotmail.com"
twitter: "dvillasanao"
github:  "dvillasanao"
linkedin: "dvillasanao"
headcolor: 009ACD
date: "`r format(Sys.time(), '%Y')`"
output:
  vitae::awesomecv:
    keep_tex: false
    includes:
      in_header: header.txt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(dplyr)
library(emojifont)
library(tidyverse)
library(fontawesome)
library(kableExtra)
library(huxtable)
library(gridExtra)
library(latexpdf)
require(tinytex)
library(googlesheets4)
#options(tinytex.verbose = FALSE)
#gs4_auth()
#https://nickstrayer.me/datadrivencv/
```

\faBookmark  \ SUMMARY
============================
Statistician specialist with skills and experience in demographic planning for the development of public policies at the national level. Among the activities conducted on a daily are the provision of specialized technical advice to different federal and local public administration agencies; as well as the updating and management of surveys, censuses, and vital statistics for the generation of socio-demographic diagnoses and research topics.  

\faGraduationCap \ EDUCATION
============================


```{r education}
googlesheets4::read_sheet('https://docs.google.com/spreadsheets/d/1zS5_1hPhYhE-T9f7FlXPP4SI5UnGy0C0BhFVqK1IBWU/edit?usp=sharing', sheet="Education") %>%
  vitae::detailed_entries(with = Title, 
                          what = Institution,
                          when = Year,
                          where = Degree, 
                          why = Details)
```


\faBook \ WORK HISTORY
============================

```{r}
googlesheets4::read_sheet('https://docs.google.com/spreadsheets/d/1zS5_1hPhYhE-T9f7FlXPP4SI5UnGy0C0BhFVqK1IBWU/edit?usp=sharing', sheet="Work History") %>%
  vitae::detailed_entries(with = Title, 
                          what = Company,
                          when = Year,
                          where = Address, 
                          why = Details)
```
\newpage  
 
\faCogs \ SKILLS
============================

```{r, eval = FALSE}
df <- googlesheets4::read_sheet('https://docs.google.com/spreadsheets/d/1zS5_1hPhYhE-T9f7FlXPP4SI5UnGy0C0BhFVqK1IBWU/edit?usp=sharing', sheet="Skills") 

## Máximo número de observaciones en las categorías
max <- max(table(df$Type))

# Repetir o agregar nuevas observaciones según sea necesario
additional_obs <- df %>%
                   mutate(Desc = NA, 
                          When = NA) %>%
                    group_by(Type) %>%
                     mutate(n = n()) %>%
                      mutate(max = max(.$n), 
                             diff = max - n) %>%
                       filter(diff != 0) %>%
                        distinct(Type, Desc, When, diff) %>%
                         slice(rep(1, each = diff)) %>%
                          select(-diff)

# Combinar los datos originales con las observaciones adicionales
combined_data <- rbind(df, additional_obs)

tabla <- combined_data%>%
          as.data.frame() %>%
           arrange(Type) %>% 
            mutate(value =  data.table::rleidv(Type), cols = rep(1:max, times = 4)) %>%
             select(-When, -value) %>%
              pivot_wider(names_from = "Type", values_from = "Desc") %>% 
               select(-cols)

tabla %>% 
 as.data.frame() %>% 
  mutate_at(vars(1:4), ~replace(., is.na(.), "")) |>
   kable(booktabs = T, align = 'c', escape = F
         ,format = "latex"
         ) |>
    kable_styling(full_width = F, 
                   font_size = 9, 
                    latex_options = "HOLD_position", 
                     html_font = "montserrat") |>
     row_spec(0, bold = T, color = "#104D93") |>
      #row_spec(1, bold = F, color = "#7f7f7f") %>%
       column_spec(column = 1:4, width = '3.5cm') |>
        row_spec(1:nrow(tabla), extra_css = "padding: 4px")

#vitae::detailed_entries(with = Type,
 #                         why = Desc,
  #                        when = When)
```

\begin{table}[H]
\centering\begingroup\fontsize{9}{11}\selectfont

\begin{tabular}{>{\centering\arraybackslash}p{3.5cm}>{\centering\arraybackslash}p{3.5cm}>{\centering\arraybackslash}p{3.5cm}>{\centering\arraybackslash}p{3.5cm}}
\toprule
\textcolor[HTML]{104D93}{\textbf{Hard Skills}} & \textcolor[HTML]{104D93}{\textbf{Language}} & \textcolor[HTML]{104D93}{\textbf{Soft Skills}} & \textcolor[HTML]{104D93}{\textbf{Software Skills}}\\
\midrule
Sampling and Census & HTML & Project Management & R\\
Survey & CSS & Verbal Communication & Python\\
Data Mining & LaTeX & Writting Communication & SPSS Statistics\\
Machine Learning & Git & Public Communication & SAS\\
Data Visualization & Markdown &  & STATA\\
\addlinespace
Public Policy &  &  & ArcGIS\\
Policy Evaluation &  &  & SQL\\
 &  &  & PowerBI | DAX\\
 &  &  & Visual Studio Code\\
 &  &  & Illustrator\\
\bottomrule
\end{tabular}
\endgroup{}
\end{table}

\faFile \ PUBLICATIONS
============================

```{r peerreviewed}
googlesheets4::read_sheet('https://docs.google.com/spreadsheets/d/1zS5_1hPhYhE-T9f7FlXPP4SI5UnGy0C0BhFVqK1IBWU/edit?usp=sharing', sheet="Publications") %>%
  #filter(category == "peer") %>%
  #select(-category) %>%
  RefManageR::as.BibEntry() %>%
  RefManageR::WriteBib("peerreviewed.bib", biblatex=T)


vitae::bibliography_entries("peerreviewed.bib") %>%
  arrange(desc(issued))
```