---
name: Diana
surname: Villasana Ocampo
position: "Actuarial Science | Statitics"
address: "Mexico City, Mexico"
email: "dvillasanao@hotmail.com"
twitter: "dvillasanao"
github:  "dvillasanao"
linkedin: "dvillasanao"
date: "`r format(Sys.time(), '%Y')`"
output:
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(googlesheets4)
#gs4_auth()
#https://nickstrayer.me/datadrivencv/
```

# SUMMARY 

Statistician specialist with skills and experience in demographic planning for the development of public policies at the national level. Among the activities conducted on a daily are the provision of specialized technical advice to different federal and local public administration agencies; as well as the updating and management of surveys, censuses, and vital statistics for the generation of socio-demographic diagnoses and research topics.  

# EDUCATION


```{r education}
googlesheets4::read_sheet('https://docs.google.com/spreadsheets/d/1zS5_1hPhYhE-T9f7FlXPP4SI5UnGy0C0BhFVqK1IBWU/edit?usp=sharing', sheet="Education") %>%
  vitae::detailed_entries(with = Title, 
                          what = Institution,
                          when = Year,
                          where = Degree, 
                          why = Details)
```


# WORK HISTORY

```{r}
googlesheets4::read_sheet('https://docs.google.com/spreadsheets/d/1zS5_1hPhYhE-T9f7FlXPP4SI5UnGy0C0BhFVqK1IBWU/edit?usp=sharing', sheet="Work History") %>%
  vitae::detailed_entries(with = Title, 
                          what = Company,
                          when = Year,
                          where = Address, 
                          why = Details)
```
 \newpage  
 
# SKILLS 

```{r}
googlesheets4::read_sheet('https://docs.google.com/spreadsheets/d/1zS5_1hPhYhE-T9f7FlXPP4SI5UnGy0C0BhFVqK1IBWU/edit?usp=sharing', sheet="Skills") %>%
  vitae::detailed_entries(with = Type,
                          why = Desc,
                          when = When)
```

# PUBLICATIONS

```{r peerreviewed}
googlesheets4::read_sheet('https://docs.google.com/spreadsheets/d/1zS5_1hPhYhE-T9f7FlXPP4SI5UnGy0C0BhFVqK1IBWU/edit?usp=sharing', sheet="Publications") %>%
  #filter(category == "peer") %>%
  #select(-category) %>%
  RefManageR::as.BibEntry() %>%
  RefManageR::WriteBib("peerreviewed.bib", biblatex=T)


vitae::bibliography_entries("peerreviewed.bib") %>%
  arrange(desc(issued))
```